\documentclass[]{article}
    \usepackage{fullpage}
    \usepackage{amsmath}
    \usepackage{amssymb}
    \usepackage{textcomp}
    \usepackage[left=0.5in, right=0.5in, top=0.7in]{geometry}
    \usepackage[utf8]{inputenc}
    \usepackage[T1]{fontenc}
    \textheight=10in
    \pagestyle{empty}
    \raggedright

    %\renewcommand{\encodingdefault}{cg}
%\renewcommand{\rmdefault}{lgrcmr}

\def\bull{\vrule height 0.8ex width .7ex depth -.1ex }

% DEFINITIONS FOR RESUME %%%%%%%%%%%%%%%%%%%%%%%

\newcommand{\lineunder} {
    \vspace*{-8pt} \\
    \hrulefill \\
}

\newcommand{\header} [1] {
    {\vspace*{6pt} \fontsize{12}{12}\selectfont \textbf{#1}}
     \lineunder
}

% END RESUME DEFINITIONS %%%%%%%%%%%%%%%%%%%%%%%

    \begin{document}
\vspace*{-40pt}

    

%==== Profile ====%
\begin{center}
	{\LARGE \scshape {Megharth Lakhataria}}\\
	Boston, MA $\cdot$ lakhataria.m@husky.neu.edu $\cdot$ (857) 869-4576 $\cdot$ www.github.com/megharth\\
\end{center}

%==== Education ====%
\header{Education}
\hspace{1mm}
\textbf{Northeastern University, Khoury College of Computer Sciences}
\hfill
Boston, MA\\
\hspace{1mm}
Masters Computer Science \textbf{GPA: 4.0/4.0} \hfill Sep 2019 - \\
\hspace{1mm}
Relevant Coursework: Web Development, Computer Systems \\
\vspace{2mm}
\hspace{1mm}
\textbf{Gujarat Technological University}\hfill Gujarat, India\\
\hspace{1mm}
Bachelors of Technology Information Technology \textbf{GPA: 9.17/10.0} \hfill
Aug 2015 - May 2019\\
\hspace{1mm}
Relevant Coursework: Operating Systems, Data Structures \\
\vspace{2mm}

%===== Skills ======%

\header{Skills}
\vspace{1mm}
\begin{tabular}{ l l }
	\textbf{Programming Languages} & Javascript, C, C++, Java, Python, HTML5, CSS3            \\
	\textbf{Databases}             & SQL, MySQL, MongoDB                                      \\
    
    \textbf{Libraries}             & Vue.js, Vuex, Elixir, Node.js, ExpressJs, React.JS,
    Redux, jQuery, Bootstrap, Laravel  \\
                          & Socket.io, GSAP, Handlebars \\
    
    \textbf{Other}                & GIT, Nginx, IntellIJ IDEA, Visual Studio Code,
    Raspberry Pi, Inkscape, Figma, Heroku \\          
\end{tabular}
\vspace{2mm}

%==== Experience ====%
\header{Experience}
\vspace{1mm}

\hspace{1mm}
\textbf{Alian Software, Anand, India}\\
\hspace{1mm}
\textit{Intern} \hfill Jan 2019 - May 2019\\
\vspace{-2mm}
\begin{itemize}
    \setlength\itemsep{0.2mm}
	\item Engineered dashboard to create metrics pertaining to orders using Amazon Marketplace API
	\item Created content management system and inventory management system to assist team with daily activities
	\item Developed customer management system to help customer care team respond to customer grievances and queries with
    minimal wait time
    \item Refined UI/UX of previous developed dashboard to ensure design consistency and better user experience for internal team
    \item Collaborated with senior developers to design and debug an interface for researchers to upload GeoTIFF images in maps to
    understand various patterns of geographical data changes resulting in data driven decision by research team
\end{itemize}
\hspace{1mm}
\textbf{Maxgen Technolgies Pvt. Ltd, Vadodara, India}\\
\hspace{1mm}
\textit{Web Developer Intern} \hfill May 2017 - July 2017\\
\vspace{-2mm}
\begin{itemize}
    \setlength\itemsep{0.2mm}
	\item Made e-commerce website using PHP, jQuery, bootstrap and MySQL
	\item Deployed WordPress to create portfolio website for various clients to increase digital footprints
\end{itemize}


%====== Projects ======%

\header{Academic Projects}
{\hspace{2mm}\textbf{Social}} {\sl React.JS, Elixir} \\

{\addtolength{\leftskip}{2mm}
A social media website that suggests potential friends based on location and
interests while supporting messaging and notifications. Implemented with an
intent to keep the target audience engaged. Achieved this by designing
Javascript and CSS3 intensive website and integrating with Facebook and
Instagram's API to keep user's basic profile in sync with these social media
platforms while attaining \textasciitilde{}80\% accuracy in finding nearby
friends. \\}
\vspace*{2mm}
{\hspace{2mm}\textbf{Checkers}} {\sl React.JS, Elixir} \\
{\addtolength{\leftskip}{2mm}
A multiplayer Checkers web-game with chat-room and game-room support. The goal
was to achieve \textasciitilde{}0\% lag and make game backups while supporting
multiple games on the server. Accomplished this by implementing Sockets that
guarantee real-time updates under stable network connection and Genservers that
stores the state of the game after every move. \\
}
\vspace*{2mm}
{\hspace{2mm}\textbf{Eye Controlled Wheelchair}} {\sl Python} \\
{\addtolength{\leftskip}{2mm}
A Raspberry Pi based prototype of eye controlled wheelchair which enables
locomotion of wheelchair using the user's eye. Aimed to achieve accurate
interpretations of user's actions and respond with minimum latency. Used
algorithms to detect the gestures of the eye, with the help of OpenCV library.
And reduced the latency between motors and Pi using L-293D H-bridge. Gained
\textasciitilde{}95\% accuracy and \textasciitilde{}20\% latency.\\
}
\vspace*{2mm}

%======= Leadership Experience ===========%
\header{Leadership Experience}
\hspace{1mm}
\textbf{Developer Head} \hfill BVM Enginerring College\\
\hspace{1mm}
Promoted for developing multiple web apps for central committee. \hfill Jul 2018
- May 2019\\
\vspace*{2mm}

\ 
\end{document}
